Efficient ancestry and mutation simulation with msprime 1.0

### 2021-09-21 cover_letter/cover_letter.tex

Since its introduction in 2016, \texttt{msprime} has grown in popularity
and is now challenging \texttt{ms} as the widely used coalescent simulator
(according to Google Scholar, \texttt{ms} has had 100 citations so far
in 2021 and \texttt{msprime} 107). This manuscript marks the important
1.0 release milestone and represents the work
of a large community. We illustrate the large range of features
that \texttt{msprime} has accumulated since the 2016 publication,
and show that performance is excellent,
often many times faster and more memory efficient than specialised
alternative simulators.

We believe that this manuscript is a summary of the state-of-the-art
in coalescent simulation, and it will be of substantial
interest to the readers of GENETICS. We hope that you agree.

>>>>

Since its introduction in 2016, \texttt{msprime} has grown in popularity
and is now challenging \texttt{ms} as the most widely used coalescent simulator
(according to Google Scholar, \texttt{ms} has had 100 citations so far
in 2021 and \texttt{msprime} 107). This manuscript marks the important
1.0 release milestone and represents the work
of a large community--the list of 32 authors represents substantial efforts from a large consortium. We illustrate the large range of features
that \texttt{msprime} has accumulated since the 2016 publication,
and show that performance is excellent,
often many times faster and more memory efficient than specialised
alternative simulators.

We believe that this manuscript is a summary of the state-of-the-art
in coalescent simulation, presents many substantial advances in this fundamental tool for popgen work, and it will be of substantial
interest to the readers of GENETICS. We hope that you agree.
